A Data-Driven Framework for Neural Field Modelling

### 2010-11-18 ltx/first_order_framework/LaTeX_Manuscript.tex
Changes to section 3.1

\ken{revise}

>>>>

\ken{revised new bit}

To reduce the computational demand of the estimation procedure, the neural field cutoff frequency was further reduced to $\boldsymbol{\nu}_{c\phi} = 0.12$~Hz. Due to the slow frequency roll-off of Gaussian basis functions an oversampling parameter of $\rho_{\phi} = 1.67$ was chosen. Therefore for an equally spaced grid of basis functions over the full spatial domain being considered, a $9\times9$ grid was required to decompose the field, which resulted in $81$ states. The other parameter of the basis functions, $\sigma_{\phi}^2$, is set based on equation \ref{eq:CutoffFromBasisFuncWidth} and the chosen neural field bandwidth $\boldsymbol{\nu}_{c\phi}$, to give $\sigma_{\phi}^2=2.5$.

\ken{how's that?}
